---
title: "Maps and methods"
author: "Simone Stevenson"
date: "04/05/2021"
output: html_document
---

```{r setup, include=FALSE}

# Load packages

## Data wrangling
library(tidyverse)
library(tidylog)

## Data visualisation
library(tmap)
library(viridisLite)

# Set up inputs

date <- Sys.Date()
today <- date
location <- "global"
country <- NA #"Australia" # If not subsetting, set as NA, e.g. country <- NA
analysis_inputs <- "N:/Quantitative-Ecology/Simone/extinction_test/outputs/version_3/2020-08-25_indicator_output_files"
save_outputs <- "yes" #only applies to maps, other things will always save
outputs <- "N:/Quantitative-Ecology/Simone/extinction_test/outputs"
timepoints <- c("2005", "2008")
manuscript_outputs <- "N:\\Quantitative-Ecology\\Simone\\extinction_test\\outputs\\version_3\\2021-05-04_manuscript_outputs"
  
dir.create(manuscript_outputs, recursive = TRUE ) # create a new directory for today's outputs
  
  
main_outputs <- file.path(manuscript_outputs, paste(date,
                                 "_main_manuscript_outputs",sep="") )
  
dir.create(main_outputs, recursive = TRUE )

supp_outputs <- file.path(manuscript_outputs, paste(date,
                                 "_supporting_info_outputs",sep="") )
  
dir.create(supp_outputs, recursive = TRUE )



indicator_values_master <- readRDS(file.path(analysis_inputs,
                          "global_ecoregions_2017_indicator_values_master.rds"))

ecoregion_values_master <- readRDS(file.path(analysis_inputs,
                               "global_ecoregions_2017_ecoregion_values_master.rds"))

ecoregion_map_all <- readRDS(paste(file.path("N:/Quantitative-Ecology/Simone/extinction_test/inputs",  "ecoregions_2017"),"Ecoregions2017valid.rds"))

ecoregion_map_data <- ecoregion_map_all %>%
                 dplyr::select(ECO_ID, ECO_NAME, OBJECTID, REALM, geometry) %>%
                      rename(ecoregion_id = ECO_ID) %>%
                      dplyr::select(ecoregion_id, geometry)

rm(ecoregion_map_all)


indicator_values_map <- indicator_values_master %>%
                        dplyr::select(ecoregion_id, indicator, year, raw_indicator_value) %>%
                        distinct(.)

indicator_map_data <- left_join(ecoregion_map_data, indicator_values_map,
                                by = "ecoregion_id")

names(indicator_map_data)

ecoregion_map_data <- ecoregion_map %>%
  rename(ecoregion_id = ECO_ID) %>%
  dplyr::select(ecoregion_id, geometry)

ecoregion_values_map <- ecoregion_values_master %>%
  dplyr::select(ecoregion_id, indicator, year, raw_indicator_value) %>%
  distinct(.)

eco_variable_map_data <- left_join(ecoregion_map_data, ecoregion_values_map,
                                by = "ecoregion_id")


```

## Biodiversity Intactness Index - Richness


```{r BII richness, echo = FALSE}


# * BII Richness ----

    rbii_data <- indicator_map_data %>%
      filter(indicator == "richness biodiversity intactness index" & year == 2005)
    
    rbii <- tm_shape(rbii_data) +
      tm_polygons(col = "raw_indicator_value",
                  border.col = "black",
                  style = "cont",
                  pal = "viridis",
                  title = "Biodiversity\nIntactness Index\n(Richness)") +
      tm_layout(legend.outside = TRUE,
                legend.outside.position = "right") 
    
    rbii
    
    tmap_save(rbii, file.path(supp_outputs, paste(today, location,
                               "richness_BII_map.png", sep = "_")),
              width=2000, height=1080, asp=0)
    
    rm(rbii, rbii_data)


```

## Biodiversity Intactness Index - Abundance

```{r BII abundance, echo = FALSE}
# * BII Abundance ----

    abii_data <- indicator_map_data %>%
      filter(indicator == "abundance biodiversity intactness index" & year == 2005)
    
    abii <- tm_shape(abii_data) +
      tm_polygons(col = "raw_indicator_value",
                  border.col = "black",
                  style = "cont",
                  pal = "viridis",
                  title = "Biodiversity\nIntactness Index\n(Abundance)") +
      tm_layout(legend.outside = TRUE,
                legend.outside.position = "right") +
      tm_borders(lwd = 0.5)
    
    abii
    
    tmap_save(abii, file.path(supp_outputs, paste(today, location,
                              "abundance_BII_map.png", sep = "_")),
              width=2000, height=1080, asp=0)
    
    rm(abii_data, abii)
    ```
    
## BHI Plants 

```{r BHI, echo = FALSE}

    bhi_data <- indicator_map_data %>%
      filter(indicator == "BHI plants" & year == 2005)
    
    bhi <- tm_shape(bhi_data) +
      tm_polygons(col = "raw_indicator_value",
                  border.col = "black",
                  style = "cont",
                  pal = "viridis",
                  title = "Biodiversity\nHabitat Index\n(Plants)") +
      tm_layout(legend.outside = TRUE,
                legend.outside.position = "right") 
    
    bhi
    
    tmap_save(bhi, file.path(indicator_outputs, paste(location,
                            "BHI_plants_map.png", sep = "_")),
              width=1920, height=1080, asp=0)

rm(bhi, bhi_data)

```

# Proportion threatened

```{r proportion threatened, echo = FALSE}
threatened_data <- indicator_map_data %>%
              filter(indicator == "proportion at risk" & year == 2008)

threatened <- tm_shape(threatened_data) +
              tm_polygons(col = "raw_indicator_value",
                           border.col = "black",
                           style = "order",
                           pal = "-viridis",
                           title = "Proportion of\nspecies threatened ") +
              tm_layout(legend.outside = TRUE,
                         legend.outside.position = "right") 

threatened

tmap_save(threatened, file.path(indicator_outputs, paste(location,
                       "proportion_threatened_map.png", sep = "_")),
                       width=1920, height=1080, asp=0)

rm(threatened, threatened_data)
```

## Proportion extinct 

```{r proportion extinct, echo = FALSE}
extinct_data <- indicator_map_data %>%
  filter(indicator == "proportion extinct" & year == 2008) 
# %>%
#   mutate(raw_indicator_value = ifelse(raw_indicator_value == 0,
#                                       NA, raw_indicator_value))

extinct <- tm_shape(extinct_data) +
           tm_polygons(col = "raw_indicator_value",
                       border.col = "black",
                       style = "fixed",
                       breaks = c(0,0,0.01, 0.02, 0.03, 0.04, 
                                  0.05, 0.06, 0.07, 0.08, 0.09, 0.1),
                       pal = "-viridis",
                       title = "Proportion of\nspecies extinct",
                       alpha = 0.8,
                       lwd = 0.1, 
                       colorNA = "grey") +
           tm_layout(legend.outside = TRUE,
                     legend.outside.position = "right") 

extinct

tmap_save(extinct, file.path(indicator_outputs, paste(location,
                   "proportion_extinct_map.png", sep = "_")),
          width=1920, height=1080, asp=0)

rm(extinct_data, extinct)
```

## Number extinct

```{r number extinct, echo = FALSE}
# * Number extinct ----

num_extinct_data <- indicator_map_data %>%
  filter(indicator == "number extinct" & year == 2008) 


num_extinct <- tm_shape(num_extinct_data) +
  tm_polygons(col = "raw_indicator_value",
              border.col = "black",
              style = "order",
              pal = "-viridis",
              title = "Number of\nspecies extinct") +
  tm_layout(legend.outside = TRUE,
            legend.outside.position = "right") 

num_extinct

tmap_save(num_extinct, file.path(indicator_outputs, paste(location,
          "number_extinct_map.png", sep = "_")),
          width=1920, height=1080, asp=0)

rm(num_extinct_data, num_extinct)

```

# Red List Index (all taxa)

```{r RLI all, echo = FALSE}
# * RLI ----

# ** All groups ----

rli_data <- indicator_map_data %>%
  filter(indicator == "RLI" & year == 2008)

rli <- tm_shape(rli_data) +
  tm_polygons(col = "raw_indicator_value",
              border.col = "black",
              style = "order",
              pal = "viridis",
              title = "Red List Index") +
  tm_layout(legend.outside = TRUE,
            legend.outside.position = "right") 

rli

tmap_save(rli, file.path(indicator_outputs, paste(location,
               "RLI_map.png", sep = "_")),
          width=1920, height=1080, asp=0)

rm(rli_data, rli)
```

## Red List Index Birds

```{r RLI birds, echo = FALSE}
bird_rli_data <- indicator_map_data %>%
  filter(indicator == "RLI-birds" & year == 2008)

bird_rli <- tm_shape(bird_rli_data) +
  tm_polygons(col = "raw_indicator_value",
              border.col = "black",
              style = "order",
              pal = "viridis",
              title = "Bird Red List Index") +
  tm_layout(legend.outside = TRUE,
            legend.outside.position = "right") 

bird_rli

tmap_save(bird_rli, file.path(indicator_outputs, paste(location,
                                                  "bird_RLI_map.png", sep = "_")),
          width=1920, height=1080, asp=0)

rm(bird_rli_data, bird_rli)
```

## Red List Index Mammals

```{r BII abundance, echo = FALSE}
# ** Mammal RLI ----

mammal_rli_data <- indicator_map_data %>%
  filter(indicator == "RLI-mammals" & year == 2008)

mammal_rli <- tm_shape(mammal_rli_data) +
  tm_polygons(col = "raw_indicator_value",
              border.col = "black",
              style = "order",
              pal = "viridis",
              title = "Mammal Red List Index") +
  tm_layout(legend.outside = TRUE,
            legend.outside.position = "right") 

mammal_rli

tmap_save(mammal_rli, file.path(indicator_outputs, paste(location,
                                                       "mammal_RLI_map.png", sep = "_")),
          width=1920, height=1080, asp=0)

rm(mammal_rli_data, mammal_rli)

```

## Red List Index Amphibians

```{r rli amphibians, echo = FALSE}
# ** Amphibian RLI ----

amphibian_rli_data <- indicator_map_data %>%
  filter(indicator == "RLI-amphibians" & year == 2008)

amphibian_rli <- tm_shape(amphibian_rli_data) +
  tm_polygons(col = "raw_indicator_value",
              border.col = "black",
              style = "order",
              pal = "viridis",
              title = "Amphibian Red List Index") +
  tm_layout(legend.outside = TRUE,
            legend.outside.position = "right") 

amphibian_rli

tmap_save(amphibian_rli, file.path(indicator_outputs, paste(location,
                                                       "amphibian_RLI_map.png", sep = "_")),
          width=1920, height=1080, asp=0)

rm(amphibian_rli_data, amphibian_rli)

```

## Human Footprint Index

```{r hfp, echo = FALSE}
# * HFP ----

hfp_data <- indicator_map_data %>%
  filter(indicator == "mean human footprint index" & year == 2005)

hfp <- tm_shape(hfp_data) +
  tm_polygons(col = "raw_indicator_value",
              border.col = "black",
              style = "order",
              pal = "-viridis",
              title = "Human\nFootprint Index") +
  tm_layout(legend.outside = TRUE,
            legend.outside.position = "right") 

hfp

tmap_save(hfp, file.path(indicator_outputs, paste(location,
                         "human_footprint_map.png", sep = "_")),
          width=1920, height=1080, asp=0)

rm(hfp_data, hfp)
```

## Living Planet Index

```{r LPI, echo = FALSE}
# * LPI ----

lpi_map_data <- indicator_map_data %>%
  filter(indicator == "LPI" & year == 2005) %>%
  st_drop_geometry()

lpi_map_data <- ecoregion_map[c("ECO_ID", "geometry")] %>%
            merge(lpi_map_data, by.x = "ECO_ID", by.y = "ecoregion_id" ,
                  all.x = TRUE) %>%
            mutate(indicator = "LPI")

head(lpi_map_data)

lpi <- tm_shape(lpi_map_data) +
       tm_polygons(col = "raw_indicator_value",
                    border.col = "black",
                    style = "order",
                    pal = "viridis",
                    title = "Living Planet Index") +
       tm_layout(legend.outside = TRUE,
                  legend.outside.position = "right") 

lpi

tmap_save(lpi, file.path(indicator_outputs, paste(location,
                          "LPI_map.png", sep = "_")),
          width=1920, height=1080, asp=0)

rm(lpi_data, lpi)
```

# Ecoregion variables

## Islands
```{r islands, echo = FALSE}

# * Islands ----

island_data <- eco_variable_map_data %>%
  filter(indicator == "island status")

island <- tm_shape(island_data) +
  tm_polygons(col = "raw_indicator_value",
              border.col = "black",
              pal = "-viridis",
              title = "Island status",
              colorNA = "grey",
              alpha = 0.8,
              lwd = 0.05) +
  tm_layout(legend.outside = TRUE,
            legend.outside.position = "right",
            bg.color = "lightblue1") 

island

tmap_save(island, file.path(indicator_outputs, paste(location,
                                                    "island_map.png", sep = "_")),
          width=1920, height=1080, asp=0)

rm(island, island_data)
```

## Biomes

```{r biomes, echo = FALSE}
biome_data <- eco_variable_map_data %>%
  filter(indicator == "Biome")

biome <- tm_shape(biome_data) +
  tm_polygons(col = "raw_indicator_value",
              border.col = "black",
              pal = "viridis",
              title = "Biome",
              colorNA = "grey",
              alpha = 0.8) +
  tm_layout(legend.outside = TRUE,
            legend.outside.position = "right") 

biome

tmap_save(biome, file.path(indicator_outputs, paste(location,
          "biome_map.png", sep = "_")),
          width=1920, height=1080, asp=0)

rm(biome, biome_data)
```

## Realms

```{r realms, echo = FALSE}

realm_data <- eco_variable_map_data %>%
  filter(indicator == "realm")

realm <- tm_shape(realm_data) +
  tm_polygons(col = "raw_indicator_value",
              style = "cont",
              border.col = "black",
              pal = "viridis",
              title = "Realm",
              colorNA = "grey",
              alpha = 0.8) +
  tm_layout(legend.outside = TRUE,
            legend.outside.position = "right") 

realm

tmap_save(realm, file.path(indicator_outputs, paste(location,
          "realm_map.png", sep = "_")),
          width=1920, height=1080, asp=0)

rm(realm, realm_data)

```

## Number of RLI records

```{r BII abundance, echo = FALSE}
rli_record_data <- eco_variable_map_data %>%
  filter(indicator == "RLI_records") %>%
  mutate(raw_indicator_value = as.numeric(raw_indicator_value))

rli_record <- tm_shape(rli_record_data) +
  tm_polygons(col = "raw_indicator_value",
              style = "order",
              border.col = "black",
              pal = "viridis",
              title = "RLI records",
              colorNA = "grey",
              alpha = 0.8) +
  tm_layout(legend.outside = TRUE,
            legend.outside.position = "right") 

rli_record

tmap_save(rli_record, file.path(indicator_outputs, paste(location,
          "rli_record_map.png", sep = "_")),
          width=1920, height=1080, asp=0)

rm(rli_record, rli_record_data)
```

## Predominant threat type

```{r BII abundance, echo = FALSE}
threat_data <- eco_variable_map_data %>%
  filter(indicator == "predominant threat type")

threat <- tm_shape(threat_data) +
  tm_polygons(col = "raw_indicator_value",
              border.col = "black",
              pal = "viridis",
              title = "Predominant threat type",
              colorNA = "grey",
              alpha = 0.8) +
  tm_layout(legend.outside = TRUE,
            legend.outside.position = "bottom") 

threat

tmap_save(threat, file.path(indicator_outputs, paste(location,
                  "predominant_threat_map.png", sep = "_")),
          width=1920, height=1080, asp=0)

rm(threat, threat_data)
```

## Headline threat type

```{r BII abundance, echo = FALSE}
headline_threat_data <- eco_variable_map_data %>%
  filter(indicator == "headline threat type")

headline_threat <- tm_shape(headline_threat_data) +
  tm_polygons(col = "raw_indicator_value",
              border.col = "black",
              pal = "viridis",
              title = "Headline threat type",
              colorNA = "grey",
              alpha = 0.8) +
  tm_layout(legend.outside = TRUE,
            legend.outside.position = "right") 

headline_threat

tmap_save(headline_threat, file.path(indicator_outputs, paste(location,
           "headline_threat_map.png", sep = "_")),
          width=1920, height=1080, asp=0)

rm(headline_threat, headline_threat_data)

```

## Included in HFP

```{r included in hfp, echo = FALSE}
incl_hfp_data <- eco_variable_map_data %>%
  filter(indicator == "included in HFP")

incl_hfp <- tm_shape(incl_hfp_data) +
  tm_polygons(col = "raw_indicator_value",
              border.col = "black",
              pal = "viridis",
              title = "Included in HFP",
              colorNA = "grey",
              alpha = 0.8) +
  tm_layout(legend.outside = TRUE,
            legend.outside.position = "right") 

incl_hfp

tmap_save(incl_hfp, file.path(indicator_outputs, paste(location,
          "hfp_inclusion_map.png", sep = "_")),
          width=1920, height=1080, asp=0)

rm(incl_hfp, incl_hfp_data)

```

## Number of endemics

```{r BII abundance, echo = FALSE}
endemics_data <- eco_variable_map_data %>%
  filter(indicator == "number of endemics")%>%
  mutate(raw_indicator_value = as.numeric(raw_indicator_value))

endemics <- tm_shape(endemics_data) +
  tm_polygons(col = "raw_indicator_value",
              border.col = "black",
              style = "fixed",
              breaks = c(0, 0, 1, 5,10, 15, 20, 25, 30, 80),
              pal = "viridis",
              title = "Number of endemics",
              colorNA = "grey",
              alpha = 0.8) +
  tm_layout(legend.outside = TRUE,
            legend.outside.position = "right") 

endemics

tmap_save(endemics, file.path(indicator_outputs, paste(location,
          "endemics_map.png", sep = "_")),
          width=1920, height=1080, asp=0)

rm(endemics, endemics_data)

```

## Mean human population density

```{r human, echo = FALSE}

human_pop_data <- eco_variable_map_data %>%
  filter(indicator == "mean human population density")%>%
  mutate(raw_indicator_value = as.numeric(raw_indicator_value))

human_pop <- tm_shape(human_pop_data) +
  tm_polygons(col = "raw_indicator_value",
              style = "log10_pretty",
              border.col = "black",
              pal = "viridis",
              title = "Mean human population density",
              colorNA = "grey",
              alpha = 0.8) +
  tm_layout(legend.outside = TRUE,
            legend.outside.position = "right") 

human_pop

tmap_save(human_pop, file.path(indicator_outputs, paste(location,
          "human_population_map.png", sep = "_")),
          width=1920, height=1080, asp=0)

rm(human_pop, human_pop_data)

```

## Number of LPI records

```{r lpi records, echo = FALSE}

lpi_records_data <- eco_variable_map_data %>%
  filter(indicator == "LPI_records") %>%
  mutate(raw_indicator_value = as.numeric(raw_indicator_value))

lpi_records <- tm_shape(lpi_records_data) +
  tm_polygons(col = "raw_indicator_value",
              style = "fixed",
              breaks = c(0, 0, 25, 50, 100, 200, 300, 400),
              border.col = "black",
              pal = "viridis",
              title = "LPI records",
              colorNA = "grey",
              alpha = 0.8) +
  tm_layout(legend.outside = TRUE,
            legend.outside.position = "right") 

lpi_records

tmap_save(lpi_records, file.path(indicator_outputs, paste(location,
          "lpi_records_map.png", sep = "_")),
          width=1920, height=1080, asp=0)

rm(lpi_records, lpi_records_data)
```

# Disturbance year

```{r disturbance year, echo = FALSE}

anthrome_data <- eco_variable_map_data %>%
  filter(indicator == "disturbance year")

anthrome <- tm_shape(anthrome_data) +
  tm_polygons(col = "raw_indicator_value",
              border.col = "black",
              pal = "viridis",
              title = "Disturbance year",
              colorNA = "grey",
              alpha = 0.8) +
  tm_layout(legend.outside = TRUE,
            legend.outside.position = "right") 

anthrome

tmap_save(anthrome, file.path(indicator_outputs, paste(location,
                              "disturbance_year_map.png", sep = "_")),
          width=1920, height=1080, asp=0)

rm(anthrome, anthrome_data)

```

## High beta diversity 

```{r beta, echo = FALSE}
beta_data <- eco_variable_map_data %>%
  filter(indicator == "High beta area")

beta_data$raw_indicator_value <- as.numeric(beta_data$raw_indicator_value)

beta <- tm_shape(beta_data) +
        tm_polygons(col = "raw_indicator_value",
                    border.col = "black",
                    style = "cont",
                    pal = "viridis",
                    title = "High beta area km^2",
                    colorNA = "grey",
                    alpha = 0.8) +
        tm_layout(legend.outside = TRUE,
                  legend.outside.position = "right") 

beta


tmap_save(beta, file.path(indicator_outputs, paste(location,
                              "beta_diversity_map.png", sep = "_")),
          width=1920, height=1080, asp=0)
```

